%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.
    % The font could be set to Windows-specific Calibri by using the 'calibri' option
    \documentclass[]{mcdowellcv}

    % For mathematical symbols
    \usepackage{amsmath}

  
    % Set applicant's personal data for header
    \name{Hanuman Huda}
    \address{Bengaluru, KA \linebreak 9642594019}
    \contacts{hanumanramhuda96@gmail.com \linebreak www.linkedin.com/in/hanumanhuda}
  

    \begin{document}
% Print the header
\makeheader
\begin{cvsection}{Experience}
    \begin{cvsubsection}{Software Engineer II} {Twitter}{Jan, 2021 - Present}
    \begin{itemize}%
        \item Responsible for building modern Identity and Access Management systems.
    \end{itemize}
    \end{cvsubsection}
	\begin{cvsubsection}{Associate}{Goldman Sachs}{June, 2017- Dec, 2020}
		            
		
		    Was responsible for complete SDLC model of Web Authentication services(Simple password, SPNEGO and RSA based)  and MIT Kerberos which is used for authentication by the entire firm.
	\begin{itemize}%
	        \item \textbf{Ping Identity in Cloud:} Designed and developed infrastructure to deploy Ping Identity in Cloud.
		    \item \textbf{Sync Services:} Designed, led and developed loosly coupled Microservices to hydrate user's profiles and credentials data from on-premise to cloud for first time and incrementally.
		    
		    \item \textbf{MIT Kerberos}
		    \begin{itemize}%
		    \item  [$\bullet$] Designed and developed REST services on top of Kerberos to allow service account provisioning through Infrastructure-as-Code.
		    \item [$\bullet$] Upgraded MIT Kerberos from 1.15.2 to 1.17.1 to improve security and availability to 99.999\%.
		    \item [$\bullet$] Scaled MIT Kerberos Infrastructure by 320\% through Horizontal and Vertical Scaling of Kerberos.
		    \item [$\bullet$] Designed and developed loosly coupled Logs Streaming Pipeline by using Filebeat, Kafka and ELK, which improved availability of the service and accuracy of audits to  100\%. 
		    \end{itemize}
		    
		     \item  \textbf{Web Authentication \& SSO}
		    \begin{itemize}%
		    
        	\item [$\bullet$]Developed REST services to onboard new teams for centralized authentication.
		    \item [$\bullet$]Completed a smooth migration of authentication services to a new and improved infrastructure, which involved collaboration with 25 teams.
		    \item [$\bullet$]Upgraded internet facing applications for authentication with Apache(httpd), Tomcat, improved security for cookies, protected pages from enumeration, introduced Rate Limiting and fixed security risks around authentication.
		   \end{itemize}
            \item \textbf{SSL Certificate Renewal:}Developed an application to automate the renewal of SSL certificates.
            
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Summer Intern}{Goldman Sachs}{May, 2016- July, 2016}
		            
		\begin{itemize}%
			\item Developed R based Risk Profiling engine to analyze the process and netstat data from all the servers.
			\item Modelled the process and netstat data to visualize the architecture of applications.
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Education}
	\begin{cvsubsection}{Warangal}{National Institute of Technology}{Aug, 2013-May, 2017}
		\begin{itemize}
			\item B. Tech. in Computer Science and Engineering. GPA: 8.11
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}

\begin{cvsection}{Technical Skills}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\item \textbf{Programming languages:}  C, C++, Java, PHP, Python(beginner), R, Assembly, SQL, Bash Script, Angular JS, React-Redux(beginner)
			\item \textbf{Databases:} Cassandra, Elastic Search, Sybase, MySQL, MongoDB
			\item \textbf{Frameworks/Tools:} Spring Boot, Django(beginner), DropWizard, Filebeat, ELK, Kafka, JMeter, AWS(beginner)  
			\item \textbf{Operating systems:}  Ubuntu, Windows 
		 
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Projects}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\setlength\itemsep{3pt}
		\item {\textbf{Exam Module}} Developed a web application using PHP, MySQL, AngularJS and Bootstrap to manage examinations of the college. It included features like eligibility check for any exam, auto-calculation of grades, student marks, grade approval from faculty to Dean and student promotion
			\item \textbf{Analysis of the Performance of DNA Sequence Compression Algorithms} Developed an algorithm to analyze the performance between ERGC(Efficient Referential Genome Compression) algorithm and NRGC (Novel Referential Genome Compression) algorithm. Paper published in HELIX Conference (https://bit.ly/2TO2jLb).
			\item \textbf{P2P} Developed Web based P2P file sharing application build on data channel API.
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Honors and Achievements}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\setlength\itemsep{3pt} 
			\item Got an accelerated promotion in Goldman Sachs  for outstanding performance.
			\item Lead Web Developer at WSDC(Web and Software Development Cell), NIT Warangal, 2016-17.
			\item 3rd position in college in Microsoft Online Hacking Competition ‘Build The Shield' , 2016
			\item AIR 4519 out of 12 lakh candidates in JEE Main, 2013.
			\item Ranked 28th among 1.5 lakh students in intermediate Rajasthan Board,2013.
            
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\end{document}